The title

### 2021-02-25 Manuscript.Rmd
This is a long due commit after running analysis and moving things to papaja

---
title: "Data Responsive-report"
author: "Ouafaa Hmaddi"
date: "January 18, 2021"
output: html_document 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("devtools")
#devtools::install_github("crsh/papaja")
```

```{r}

#load libraries
#if (!requireNamespace("BiocManager", quietly = TRUE))
#install.packages("caret")

#BiocManager::install("preprocessCore")

library(rio)
library(tidyverse)
library(lubridate)
library(janitor)
library(ggplot2)
library(readxl)
library(reshape2)
library(readr)
library(psych)
library(foreign)
library(plm)
library(lme4)
library(lattice)
library(lmerTest)
library(EFAutilities)
library(haven)
library(sjPlot)
library(XLConnect)
library(preprocessCore)
library(knitr)
library(caret)

@@

```{r Countries to analyse in main sample}
gali <- import("Data/GALI_External_DataRelease_2020.xlsx")

@@

#X countries have fewer than 50 firms in the sample. Because so few observations may not offer good representation, I excluded firms headquartered in these countries from the analysis, keeping X firms in Y countries and Z industries.

@@

#Number of ventures in main sample 
#kable(countries_to_keep)

@@

```{r}
gali <- filter(gali, found_name1_age > 14 | is.na(found_name1_age))
gali <- filter(gali, found_name2_age > 14 | is.na(found_name2_age))
gali <- filter(gali, found_name3_age > 14 | is.na(found_name3_age))
gali <- filter(gali, found_name1_age < 70 | is.na(found_name1_age))
gali <- filter(gali, found_name2_age < 70 | is.na(found_name2_age))
gali <- filter(gali, found_name3_age < 70 | is.na(found_name3_age))

@@

```{r Countries to keep in sample with valid data}

@@

#Number of ventures in main sample 
#kable(countries_to_keep)
```

#GEM NES Data

```{r}
gem_nes <- import("Data/GEM-NES.csv")

#Clean and tidy gem NES
gem_nes <- clean_names(gem_nes)
gem_nes <- gem_nes %>%
  row_to_names(row_number = 2)

gem_nes[,-2] <- gem_nes[,-2] %>% mutate_if(is.character,as.numeric)

gem_nes$inst_hc_nes <- rowMeans(gem_nes[,(5:6)])
gem_nes <- clean_names(gem_nes)
gem_nes <- gem_nes %>%
  rename(country = economy) %>%
  rename(inst_fc_gem = 	financing_for_entrepreneurs)

gem_nes <- gem_nes [, -(5:6)]

#Normalize NES data (all data is based on a scale from 1 to 5)
mean_norm_minmax <- function(x){
                                (x- mean(x)) /(max(x)-min(x))
                               }

mean_norm_nes <- as.data.frame(lapply(gem_nes[,(4:5)], mean_norm_minmax))

gem_nes <- cbind(gem_nes[, (1:3)], mean_norm_nes)

@@

#GEM APS data

```{r}
#gem_aps <- import("Data/GEM-APS.csv")
#Clean and tidy gem APS
#gem_aps <- clean_names(gem_aps)
#gem_aps <- gem_aps %>%
  #row_to_names(row_number = 2)
#gem_aps[,-2] <- gem_aps[,-2] %>% mutate_if(is.character,as.numeric)
#gem_aps <- clean_names(gem_aps)
#gem_aps <- gem_aps %>%
  #rename(country = economy) %>%
  #rename(inst_signaling_aps = high_status_to_successful_entrepreneurs) #%>%
  #rename(inst_hc_aps = established_business_ownership) %>%
  #rename(inst_sc_aps = total_early_stage_entrepreneurial_activity_tea)

#All APS data is a percentage. We devide by 100 to gat [0,1] range
#gem_aps$inst_signaling_gem <- gem_aps$inst_signaling_aps /100 
#gem_aps$inst_hc_aps <- gem_aps$inst_hc_aps /100 + 1
#gem_aps$inst_sc_gem <- gem_aps$inst_sc_aps /100 + 1

#Final GEM data

```{r}
gem <- gem_nes
#join nes and aps on country and year 
#gem <- left_join(gem_nes, gem_aps, by=c("country", "year", "code"))
#gem$inst_hc_gem <- rowMeans(gem[,c("inst_hc_nes", "inst_hc_aps")]) + 1
#gem$inst_hc_gem <- gem$inst_hc_nes

#gem <- gem %>%
  #select(code, country, year, ends_with('_gem'))

gem$country[gem$country == "United States"] <-"USA"

gem <- gem %>%
  group_by(country) %>%
  mutate(inst_fc_gem = mean(inst_fc_gem, na.rm= TRUE))
#  inst_hc_gem = mean(inst_hc_gem, na.rm= TRUE),
  #inst_sc_gem = mean(inst_sc_gem, na.rm= TRUE),
#  inst_signaling_gem = mean(inst_signaling_gem, na.rm= TRUE))

#gem <- select(gem, -year, -inst_hc_nes)

gem <- gem %>% distinct()

#CGI data
```{r}
gci <- import("Data/GCI_2018.xlsx")

@@

```{r fig.height=10, fig.width=10}

@@

```{r Cleaning data of acceleration benefit ranking }

@@

#Reverse code attention variable 
```{r}
#Reverse code fundtion 
reverse <- function(x){x*-1- +8}

@@

```{r}
mean_norm_att <- as.data.frame(lapply(gali %>%
                            select(starts_with("accel_ben_rank_")), mean_norm_minmax))

@@

```{r}

#Calculating the average of different benifits to group them into one of the 3 categories of capital plus signaling.

gali$attention_hc <- round(gali$accel_ben_rank_business_skills,2)

gali$attention_sc <- round(rowMeans(gali[,
                                  c('accel_ben_rank_network',
                                'accel_ben_rank_access_entreprene')],
                              na.rm=TRUE),2)

gali$attention_fc <-  round(rowMeans(gali[,
                                  c('accel_ben_rank_direct_funding',
                                'accel_ben_rank_access_investors')],
                              na.rm=TRUE),2)

#Join all 3 datasets 
```{r}

@@

#Fiancial Capital acquisiton total
```{r}
gali_joined  <- gali_joined %>% mutate(capital_raised0 = gali_joined %>% select(starts_with("inv_") & ends_with("_m1")) %>% 
                         rowSums(na.rm = TRUE))

@@

#Revenues
```{r}
gali_joined <- gali_joined %>% mutate(revenue_tot = gali_joined %>%
                         select(contains("revenues")) %>% 
                         rowSums(na.rm = TRUE))
```

#Human capital acquisition 
```{r}
gali_joined  <- gali_joined %>% mutate(hr_tot = gali_joined %>%
                         select(contains("_employees")) %>% 
                         rowSums(na.rm = TRUE))
```

#Social capital acquisition 
```{r}
gali_joined <- gali_joined %>% mutate(equity_sources_tot = gali_joined %>%
                         select(contains("equityfrom")) %>% 
                         rowSums(na.rm = TRUE))
```

#Mixed model analysis - Human capital
```{r}
fit0hc <- lmer(participated ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)

fit1hc <- lmer(participated ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)

summary(fit0hc)
summary(fit1hc)

@@

fit11hc <- lmer(hr_tot ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)

summary(fit00hc)
summary(fit11hc)

@@

#Mixed model analysis - Financial capital
```{r}
fit0fc <- lmer(participated ~   + (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)

fit1fc <- lmer(participated ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)

fit2fc <- lmer(participated ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)

fit3fc <- lmer(participated ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country), data = gali_joined, REML = F)

@@

```{r}
fit0sc <- lmer(participated ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)

@@

summary(fit0sc)
summary(fit1sc)

@@

summary(fit00sc)
summary(fit11sc)

@@

##Constrcuting human capital index (control variable)
###Graduate percentage, Prior C-level Executive Percentage, Average Team Tenure , Team Prior Founding

```{r Human capital index}
#Graduate percentage

gali_joined$founder1_grad = ifelse(gali_joined$found_name1_education == "Masters Degree" | 
                              gali_joined$found_name1_education =="PhD" |
                              gali_joined$found_name1_education == "Some graduate degree", 1, 0) 
gali_joined$founder1_grad[is.na(gali_joined$founder1_grad)] <- 0

gali_joined$founder2_grad = ifelse(gali_joined$found_name2_education == "Masters Degree" | 
                              gali_joined$found_name2_education =="PhD" |
                              gali_joined$found_name2_education == "Some graduate degree", 1, 0) 
gali_joined$founder2_grad[is.na(gali_joined$founder2_grad)] <- 0

gali_joined$founder3_grad = ifelse(gali_joined$found_name3_education == "Masters Degree" |
                              gali_joined$found_name3_education =="PhD" |
                              gali_joined$found_name3_education == "Some graduate degree", 1, 0)
gali_joined$founder3_grad[is.na(gali_joined$founder3_grad)] <- 0

gali_joined$nb_of_founders <- gali_joined$found_name1_present + gali_joined$found_name2_present + gali_joined$found_name3_present

gali_joined <- filter(gali_joined, nb_of_founders > 0)

gali_joined$grad_pct = ((gali_joined$founder1_grad + gali_joined$founder2_grad + gali_joined$founder3_grad) / gali_joined$nb_of_founders)

#Prior C-level Executive Percentage

gali_joined$founder1_job1_clevel = ifelse(is.na(gali_joined$found_name1_job1_role) | gali_joined$found_name1_job1_role !=  "CEO/Executive Director" , 0, 1)
gali_joined$founder1_job2_clevel = ifelse(is.na(gali_joined$found_name1_job2_role) | gali_joined$found_name1_job2_role !=  "CEO/Executive Director" , 0, 1)
gali_joined$founder2_job1_clevel = ifelse(is.na(gali_joined$found_name2_job1_role) | gali_joined$found_name2_job1_role !=  "CEO/Executive Director" , 0, 1)
gali_joined$founder2_job2_clevel = ifelse(is.na(gali_joined$found_name2_job2_role) | gali_joined$found_name2_job2_role !=  "CEO/Executive Director" , 0, 1)
gali_joined$founder3_job1_clevel = ifelse(is.na(gali_joined$found_name3_job1_role) | gali_joined$found_name3_job1_role !=  "CEO/Executive Director" , 0, 1)
gali_joined$founder3_job2_clevel = ifelse(is.na(gali_joined$found_name3_job2_role) | gali_joined$found_name3_job2_role !=  "CEO/Executive Director" , 0, 1)

gali_joined$prior_clevel_pct = ((gali_joined$founder1_job1_clevel + gali_joined$founder1_job2_clevel + gali_joined$founder2_job1_clevel + 
  gali_joined$founder2_job2_clevel + gali_joined$founder3_job1_clevel + gali_joined$founder3_job2_clevel) / (gali_joined$nb_of_founders*2))

#Average Team Tenure

gali_joined$avg_teamtenure <- rowMeans(subset(gali_joined, select = c('found_name1_job1_tenure', 'found_name1_job2_tenure', 'found_name2_job1_tenure', 'found_name2_job2_tenure', 'found_name3_job1_tenure', 'found_name3_job2_tenure')), na.rm = TRUE)

gali_joined$avg_teamtenure[is.nan(gali_joined$avg_teamtenure)] <- 0

#Team Prior Founding
gali_joined$team_prior_founding <- gali_joined$found_name1_prior_fp + gali_joined$found_name2_prior_fp + gali_joined$found_name3_prior_fp + gali_joined$found_name1_prior_other + gali_joined$found_name2_prior_other + gali_joined$found_name3_prior_other + gali_joined$found_name1_prior_np + gali_joined$found_name2_prior_np + gali_joined$found_name3_prior_np

#Final Human Capital Index

gali_joined$z_team_prior_founding <- scale(gali_joined$team_prior_founding, center = TRUE, scale = TRUE)
gali_joined$z_prior_clevel_pct <- scale(gali_joined$prior_clevel_pct, center = TRUE, scale = TRUE)
gali_joined$z_avg_teamtenure <- scale(gali_joined$avg_teamtenure, center = TRUE, scale = TRUE)
gali_joined$z_grad_pct <- scale(gali_joined$grad_pct, center = TRUE, scale = TRUE)

#Cite Bolstad et al, Bioinformatics (2003)

gali_joined$normq_team_prior_founding <- normalize.quantiles(gali_joined$z_team_prior_founding,copy=TRUE)
gali_joined$normq_prior_clevel_pct <- normalize.quantiles(gali_joined$z_prior_clevel_pct,copy=TRUE)
gali_joined$normq_avg_teamtenure <- normalize.quantiles(gali_joined$z_avg_teamtenure,copy=TRUE)
gali_joined$normq_grad_pct <- normalize.quantiles(gali_joined$z_grad_pct,copy=TRUE)

#group all into an index

gali_joined$HC_index <- (gali_joined$normq_team_prior_founding + gali_joined$normq_prior_clevel_pct + gali_joined$normq_avg_teamtenure + gali_joined$normq_grad_pct)

##Constrcuting social capital index (control variable)

```{r}

##Constrcuting financial capital index (control variable)

```{r}

##Gender decomposition variable

```{r Gender decomposition variable}
gali <- gali %>% drop_na(found_name1_gender)

gali$found_name2_gender[is.na(gali$found_name2_gender)] <- 0
gali$found_name3_gender[is.na(gali$found_name3_gender)] <- 0

gali$founder1_f <- ifelse(gali$found_name1_gender == "F", 1,0)
gali$founder2_f <- ifelse(gali$found_name2_gender == "F", 1,0)
gali$founder3_f <- ifelse(gali$found_name3_gender == "F", 1,0)

gali$female_pct <- round(((gali$founder1_f + gali$founder2_f + gali$founder3_f) / gali$nb_of_founders ), 2)

```{r Capital structure study variables}

##Total invesmtment
gali_0$tot_cap_m1 <- rowSums(gali_0[ , c('inv_ownmoney_m1', 'inv_outequity_m1', 'inv_totaldebt_m1', 'inv_philan_m1')],na.rm = TRUE)

gali_0$tot_cap_sincefound <- rowSums(gali_0[ , c('inv_ownmoney_sincefound', 'inv_outequity_sincefound', 'inv_totaldebt_sincefound', 'inv_philan_sincefound')],na.rm = TRUE)

gali_0$fu1_tot_cap_m1 <- rowSums(gali_0[ , c('fu1-inv_ownmoney_m1', 'fu1-inv_outequity_m1', 'fu1-inv_totaldebt_m1', 'fu1-inv_philan_m1')],na.rm = TRUE)

##Percentage of each capital type 
###Equity
gali_0$pctequity_m1 <- gali_0$inv_outequity_m1 / gali_0$tot_cap_m1
gali_0$pctequity_sincefound <- gali_0$inv_outequity_sincefound / gali_0$tot_cap_sincefound
gali_0$fu1_pctequity_m1 <- gali_0$`fu1-inv_outequity_m` / gali_0$fu1_tot_cap_m1

###Debt
gali_0$pctdebt_m1 <- gali_0$inv_totaldebt_m1 / gali_0$tot_cap_m1
gali_0$pctdebt_sincefound <- gali_0$inv_totaldebt_sincefound / gali_0$tot_cap_sincefound
gali_0$fu1_pctdebt_m1 <- gali_0$`fu1-inv_totaldebt_m` / gali_0$fu1_tot_cap_m1

###Own Money
gali_0$pctownmoney_m1 <- gali_0$inv_ownmoney_m1 / gali_0$tot_cap_m1
gali_0$pctownmoney_sincefound <- gali_0$inv_ownmoney_sincefound / gali_0$tot_cap_sincefound
gali_0$fu1_pctownmoney_m1 <- gali_0$`fu1-inv_ownmoney_m` / gali_0$fu1_tot_cap_m1

###Phillantropy
gali_0$pctphilan_m1 <- gali_0$inv_philan_m1 / gali_0$tot_cap_m1
gali_0$pctphilan_sincefound <- gali_0$inv_philan_sincefound / gali_0$tot_cap_sincefound
gali_0$fu1_pctphilan_m1 <- gali_0$`fu1-inv_philan_m` / gali_0$fu1_tot_cap_m1

##Single source vs dominant source (> 90%)
###Single source
gali_0$single_source_m1 <- ifelse(gali_0$pctequity_m1 == 1 | 
                                  gali_0$pctdebt_m1 == 1|
                                  gali_0$pctownmoney_m1 == 1 |
                                  gali_0$pctphilan_m1 ==1 , 1, 0)

gali_0$single_source_sincefound <- ifelse(gali_0$pctequity_sincefound == 1 | 
                                  gali_0$pctdebt_sincefound == 1|
                                  gali_0$pctownmoney_sincefound == 1 |
                                  gali_0$pctphilan_sincefound ==1 , 1, 0)

gali_0$single_fu1_source_m1 <- ifelse(gali_0$fu1_pctequity_m1 == 1 | 
                                  gali_0$fu1_pctdebt_m1 == 1|
                                  gali_0$fu1_pctownmoney_m1 == 1 |
                                  gali_0$fu1_pctphilan_m1 ==1 , 1, 0)

###Dominant source
gali_0$dominant_source_m1 <- ifelse((gali_0$pctequity_m1 >= .9 | 
                                  gali_0$pctdebt_m1 >= .9 |
                                  gali_0$pctownmoney_m1 >= .9 |
                                  gali_0$pctphilan_m1 >= .9) &
                                    gali_0$single_source_m1 == 0, 1, 0)

gali_0$dominant_source_sincefound <- ifelse((gali_0$pctequity_sincefound >= .9 | 
                                  gali_0$pctdebt_sincefound >= .9 |
                                  gali_0$pctownmoney_sincefound >= .9 |
                                  gali_0$pctphilan_sincefound >= .9) &
                                  gali_0$single_source_m1 == 0, 1, 0)

gali_0$dominant_fu1_source_m1 <- ifelse((gali_0$fu1_pctequity_m1 >= .9 | 
                                  gali_0$fu1_pctdebt_m1 >= .9 |
                                  gali_0$fu1_pctownmoney_m1 >= .9 |
                                  gali_0$fu1_pctphilan_m1 >= .9) &
                                  gali_0$single_source_m1 == 0, 1, 0)
```

```{r Apirations for capital structure in 12 months and 3 years }
##Total aspired  invesmtment Pre-acceleration 
gali_0$tot_plans_cap_12m <- rowSums(gali_0[ , c('inv_plans_outequity_12months', 'inv_plans_debt_12months', 'inv_plans_philan_12months')],na.rm = TRUE)

gali_0$tot_plans_cap_3y <- rowSums(gali_0[ , c('inv_plans_outequity_3years', 'inv_plans_debt_3years', 'inv_plans_philan_3years')], na.rm = TRUE)

##Total aspired  invesmtment Post-acceleration 
gali_0$fu1_tot_plans_cap_12m <- rowSums(gali_0[ , c('fu1-inv_plans_outequity_12months', 'fu1-inv_plans_debt_12months', 'fu1-inv_plans_philan_12months')], na.rm = TRUE)

gali_0$fu1_tot_plans_cap_3y <- rowSums(gali_0[ , c('fu1-inv_plans_outequity_3years', 'fu1-inv_plans_debt_3years', 'fu1-inv_plans_philan_3years')], na.rm = TRUE)

##Aspired percentage of each capital type pre-acceleration 
###Equity
gali_0$pctequity_plan12m <- gali_0$inv_plans_outequity_12months / gali_0$tot_plans_cap_12m
gali_0$pctequity_plan3y <- gali_0$inv_plans_outequity_3years / gali_0$tot_plans_cap_3y

###Debt
gali_0$pctdebt_m1 <- gali_0$inv_plans_debt_12months / gali_0$tot_plans_cap_12m
gali_0$pctdebt_sincefound <- gali_0$inv_plans_debt_3years / gali_0$tot_plans_cap_3y

###Phillantropy
gali_0$pctphilan_m1 <- gali_0$inv_plans_philan_12months / gali_0$tot_plans_cap_12m
gali_0$pctphilan_sincefound <- gali_0$inv_plans_philan_3years / gali_0$tot_plans_cap_3y

##Aspired percentage of each capital type post-acceleration 
###Equity
gali_0$fu1_pctequity_plan12m <- gali_0$`fu1-inv_plans_outequity_12months` / gali_0$fu1_tot_plans_cap_12m
gali_0$fu1_pctequity_plan3y <- gali_0$`fu1-inv_plans_outequity_3years` / gali_0$fu1_tot_plans_cap_3y

###Debt
gali_0$fu1_pctdebt_plan12m <- gali_0$`fu1-inv_plans_debt_12months` / gali_0$fu1_tot_plans_cap_12m
gali_0$fu1_pctdebt_plan3y <- gali_0$`fu1-inv_plans_debt_3years` / gali_0$fu1_tot_plans_cap_3y

###Phillantropy
gali_0$fu1_pctphilan_plan12m <- gali_0$`fu1-inv_plans_philan_12months` / gali_0$fu1_tot_plans_cap_12m
gali_0$fu1_pctphilan_plan3y <- gali_0$`fu1-inv_plans_philan_3years` / gali_0$fu1_tot_plans_cap_3y

>>>>

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "Ouafaa Hmaddi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "ohmaddi@uoregon.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "University of Oregon"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.
```{r message=FALSE, warning=FALSE, include=FALSE}
library(rio)
library(tidyverse)
library(janitor)
library(ggplot2)
library(psych)
library(knitr)

@@

```{r Countries to analyse in main sample, message=FALSE, warning=FALSE, include=FALSE}
gali <- import("Data/GALI_External_DataRelease_2020.xlsx")

@@

@@

@@

```{r message=FALSE, warning=FALSE, include=FALSE}
gali <- filter(gali, found_name1_age > 14 | is.na(found_name1_age))
gali <- filter(gali, found_name2_age > 14 | is.na(found_name2_age))
gali <- filter(gali, found_name3_age > 14 | is.na(found_name3_age))
gali <- filter(gali, found_name1_age < 70 | is.na(found_name1_age))
gali <- filter(gali, found_name2_age < 70 | is.na(found_name2_age))
gali <- filter(gali, found_name3_age < 70 | is.na(found_name3_age))

@@

```{r Countries to keep in sample with valid data, message=FALSE, warning=FALSE, include=FALSE}

@@

@@

#CGI data
```{r message=FALSE, warning=FALSE, include=FALSE}
gci <- import("Data/GCI_2018.xlsx")

@@

```{r echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}

@@

```{r Cleaning data of acceleration benefit ranking, message=FALSE, warning=FALSE, include=FALSE}

@@

#Reverse code attention variable 
```{r message=FALSE, warning=FALSE, include=FALSE}
#Reverse code fundtion 
reverse <- function(x){x*-1- +8}

@@

```{r message=FALSE, warning=FALSE, include=FALSE}

mean_norm_minmax <- function(x){
                                (x- mean(x)) /(max(x)-min(x))
                               }

mean_norm_att <- as.data.frame(lapply(gali %>%
                            select(starts_with("accel_ben_rank_")), mean_norm_minmax))

@@

#Join all 3 datasets 
```{r message=FALSE, warning=FALSE, include=FALSE}

@@

#Fiancial Capital acquisiton total
```{r message=FALSE, warning=FALSE, include=FALSE}
gali_joined  <- gali_joined %>% mutate(capital_raised0 = gali_joined %>% select(starts_with("inv_") & ends_with("_m1")) %>% 
                         rowSums(na.rm = TRUE))

@@

#Revenues
```{r message=FALSE, warning=FALSE, include=FALSE}
gali_joined <- gali_joined %>% mutate(revenue_tot = gali_joined %>%
                         select(contains("revenues")) %>% 
                         rowSums(na.rm = TRUE))
```

#Human capital acquisition 
```{r message=FALSE, warning=FALSE, include=FALSE}
gali_joined  <- gali_joined %>% mutate(hr_tot = gali_joined %>%
                         select(contains("_employees")) %>% 
                         rowSums(na.rm = TRUE))
```

#Social capital acquisition 
```{r message=FALSE, warning=FALSE, include=FALSE}
gali_joined <- gali_joined %>% mutate(equity_sources_tot = gali_joined %>%
                         select(contains("equityfrom")) %>% 
                         rowSums(na.rm = TRUE))
```

# Results

```{r message=FALSE, warning=FALSE, include=FALSE}
#Function to extract coefficients of summary table

summary_table <- function(x){ x$coefficients %>%
  as.data.frame %>%
    rename(
      "$b$" = "Estimate"
    , "SE" = "Std. Error"
    , "$t$" = "t value"
  ) %>%
  mutate(
    Effect = papaja:::prettify_terms(rownames(.))
  ) %>%
  printnum(
    digits = c(2, 2, 2, 3)
    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
  ) %>%
  select(Effect, `$b$`, `SE`, `$t$`)}

#for glmer

summary_table_z <- function(x){ x$coefficients %>%
  as.data.frame %>%
    rename(
      "$b$" = "Estimate"
    , "SE" = "Std. Error"
    , "$z$" = "z value"
  ) %>%
  mutate(
    Effect = papaja:::prettify_terms(rownames(.))
  ) %>%
  printnum(
    digits = c(2, 2, 2, 3)
    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
  ) %>%
  select(Effect, `$b$`, `SE`, `$z$`)}

#Mixed model analysis - Human capital
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(lme4)
fit0hc <- glmer(participated ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, family=binomial)

fit1hc <- glmer(participated ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, family=binomial)

@@

fit11hc <- lmer(hr_tot ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)
hc0 <- summary_table_z(summary(fit0hc))
hc1 <- summary_table_z(summary(fit1hc))
hc00 <- summary_table(summary(fit00hc))
hc11 <- summary_table(summary(fit11hc))

rownames(hc0) <- c("Intercept","Attention to Human capital(AHC)")
rownames(hc1) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
rownames(hc00) <- c("Intercept","Attention to Human capital")
rownames(hc11) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")

kable(hc0[,-1]) 
kable(hc1[,-1])
kable(hc00[,-1])
kable(hc11[,-1])

@@

#Mixed model analysis - Financial capital
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(lme4)
fit0fc <- glmer(participated ~  accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding|country), data = gali_joined, family=binomial)

fit1fc <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country ), data = gali_joined, family=binomial)

fit2fc <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country ), data = gali_joined, family=binomial)

fit3fc <- glmer(participated ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country), data = gali_joined, family=binomial)

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
fit0sc <- lmer(participated ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)

@@

coef(summary(fit0sc))
coef(summary(fit1sc))

@@

coef(summary(fit00sc))
coef(summary(fit11sc))

@@

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
